% Author: Cristian Gonzales %%%%%%%%%%%%%%

\documentclass{res}

\usepackage[margin=0.1in, right=30mm]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{multicol}

% Magic that makes errors form collusion of resume class and header/footer:
% https://tex.stackexchange.com/questions/105586/footer-not-appearing-on-resume
\textheight=10in
\footskip=25pt
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot[C]{} % other info in "inner" position of footer line
\pagestyle{fancy}

\begin{document}
\begin{resume}

% Header
\begin{center}
\textsc{{\Huge Cristian Gonzales}}\\
\vspace{1mm}
\textsc{\large Software Engineer at Northrop Grumman}\\
\vspace{1mm}
\end{center}

% Links
\begin{multicols}{4}
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\faLinkedinSquare\ 
\textit{https://bit.ly/eey7W}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%
\columnbreak
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\faGithub\ 
\textit{https://bit.ly/2McyUX}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%
\columnbreak
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\faGlobe\ 
\textit{https://bit.ly/2vA649}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%
\columnbreak
%%%%%%%%%%%%%%%%%%%%%%%%
\faEnvelope\ 
\textit{xcristian.gonzales@gmail.com}
%%%%%%%%%%%%%%%%%%%%%%%%
\end{multicols}

\vspace{-3mm}

% Experience
\textsc{{\Large Experience}}
\vspace{0.5mm}
\hrule width18.5cm
%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Northrop Grumman}\\
\textit{Associate Software Engineer}
\hfill
July 2019 -- Present\\[1mm]
	\begin{itemize}
		\vspace{-3mm}
    \item Developed an API to filter JMS messages from a legacy JMS service, using Google Guice injections to differentiate between different instances of the service and JAXB for object serialization to send messages across the wire.
    \item Refactored database schemas and their associated JPA mappings, along with protocol buffer definitions, to differentiate between different satellite missions for a server-side event message syslog implementation, where the mission identifier was injected using Google Guice.
    \item Developed Jenkins CI/CD pipelines to streamline build processes in different target environments--–namely, Linux, Solaris, and Windows--decreasing the time of the build and release process from four days to two hours.
    \item Developed shell and Perl scripts to streamline build and release processes, along with artifact repository management and Jenkins job versioning, tailored for both humans outside of a CI/CD pipeline and a Jenkins daemon.
    \item Promoted Agile methodologies, as a Scrum Master, by leading daily Scrum meetings, retrospectives, and planning in a program-wide effort to migrate away from a waterfall model.
    \item Automated deployment for builds for ad hoc projects and ported build systems from Apache Ant to Apache Maven.
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{Northrop Grumman}\\
\textit{Software Engineering Intern}
\hfill
June 2017 -- August 2017\\[1mm]
	\begin{itemize}
		\vspace{-3mm}
  \item Interfaced with NASA's GMSEC API to build a visualization tool which tracked health statuses of satellites.
  \item Ported payload data, via web sockets, across multiple Northrop Grumman domains/applications while leveraging code reuse through dependency injections, using Google Guice.
	\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%
% Projects
\textsc{{\Large Projects}}
\vspace{0.5mm}
\hrule width18.5cm
%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ShardedKVS: A Fault Tolerant and Scalable Key-Value Store}\\
\textit{A scalable, sharded Docker cluster of nodes that is fault tolerant, highly available, and eventually consistent.}
	\vspace{2mm}
	\begin{itemize}
    \item Nodes were designed using a RESTful API interface (Python Flask), so clients may use the API to add and delete nodes, and keys, from the KVS.
		\item Favors availability over strong consistency, per CAP theorem, so eventual consistency is guaranteed in light of network partitions, with a property of bounded staleness.
    \item Uses vector clocks as an implementation of causal order to resolve conflicting keys, and consistent hashing to dynamically and uniformly distribute unique keys, across all shards.
	\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{{\Large Skills}}
\vspace{0.5mm}
\hrule width18.5cm
\textsc{Languages:} Bash, C, csh, Java, JavaScript, Perl, PowerShell, Python, Swift, SQL\\[2mm]
\textsc{Build systems:} Apache Ant, Apache Maven, make\\[2mm]
\textsc{Tools:} Ansible, Docker, Eclipse, Git, \LaTeX, PostgresSQL, PyCharm, Jenkins, Xcode\\[2mm]
\textsc{Concepts:} Agile Development (Scrum framework), Operating Systems, Containerization and Virtualization, Continuous Integration/Delivery (CI/CD), DevOps, Dependency Injections, Distributed Systems, Object Relational Mapping (ORM), Publish-Subscribe Messaging Pattern, Release Engineering, RESTful APIs\\[0.5mm]
\vspace{-4mm}
%%%%%%%%%%%%%%%%%%%%%%%%

% Education
\textsc{{\Large Education}}
\vspace{0.5mm}
\hrule width18.5cm
%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{University of California, Santa Cruz}\\
\textit{Computer Science, B.S.}
\hfill
June 2016 -- June 2019\\
\vspace{-2mm}
\end{resume}
\lfoot{\textit{References available upon request.}}
\end{document}
